CogSci Analysis

### 2019-02-25 conceptNet-cogsci/Cogsci.Rmd
Added CogsciBackground
Added cluster randomization

```{r message=FALSE}
clusters_evolution <- function(vocab, n_clusters, min_age, max_age, randomization) {

  if(randomization == "none") {
    # do nothing
  } else if(randomization == "random_aoa") {
    vocab <- randomize_aoa(vocab) # TODO handle randomization, write "randomize_aoa"" in random_helper.r
  } else if(randomization == "to_nearest_aoa") {
    vocab <- randomize_aoa_to_nearest(vocab)
  } else if(randomization == "within_last_clustering") {
    vocab <- randomize_within_last_clustering(vocab, n_clusters)
  } else {
    stop("Randomization argument incorrect.")
  }

@@

  # list of cluster membership index vectors at each age
  membership_evo <- net_evo %>%
    map(w2v_waltrap) %>%
    map(~ cut_at(., no = n_clusters))

@@

@@

measure_cluster_dynamics <- function(language, n_clusters, measures, randomizations, samples) {
    vocab <- get_language_vocab(language)

@@

    # true vocabulary sizes (full vocabulary size at each month)
    measurements[["true_vocab_sizes"]] <-
      tibble(age = min(vocab$age):max(vocab$age),
             measure = "true_vocab_size",
             randomization = NA, # same for all randomizations
             sample = NA,
             value = min(vocab$age):max(vocab$age) %>%
               map(~ filter(vocab, age <= .)) %>%
               map(nrow) %>%
               unlist())

    # --------------------- true aoa measures --------------------- #
    true_clusters_evo <- clusters_evolution(vocab,
                                            n_clusters,
                                            min(vocab$age),
                                            max(vocab$age),
                                            randomization = "none")

    # w2v vocabulary sizes (number of words know at each month in clustering)
    measurements[["w2v_vocab_sizes"]] <- 
      tibble(age = min(vocab$age):max(vocab$age),
             measure = "w2v_vocab_size",
             randomization = NA, # same for all randomizations
             sample = NA,
             value = unlist(map(true_clusters_evo, ~ length(unlist(.)))))

    # dynamics measures
    for (measure in measures) {
      value <- run_measure(true_clusters_evo, measure)
      measurements[[measure]] <-
        tibble(age = min(vocab$age):max(vocab$age),
               measure = measure,
               randomization = "none",
               sample = NA,
               value = value)
    }

    # --------------------- randomized aoa measures --------------------- #
    for (randomization in randomizations) {

      for (sample in 1:samples) {
        random_clusters_evo <- clusters_evolution(vocab,
                                                  n_clusters,
                                                  min(vocab$age),
                                                  max(vocab$age),
                                                  randomization = randomization)

        for (measure in measures) {
          value <- run_measure(random_clusters_evo, measure)
          measurements[[paste(randomization, measure, sample, sep = "__")]] <-
            tibble(age = min(vocab$age):max(vocab$age),
                   measure = measure,
                   randomization = randomization,
                   sample = sample,
                   value = value)
        }
      }
    }

@@

run_experiment <- function(languages, measures, randomizations, cluster_counts, samples) {
  measurements = list()
  cat("measuring dynamics\n")
  for(language in languages) {
    cat("  language:", language, "\n")
    for(n_clusters in cluster_counts) {
      cat("    n_clusters: ", n_clusters, "\n")
      measurements[[length(measurements) + 1]] <- 
        measure_cluster_dynamics(language, n_clusters, measures, randomizations, samples) %>%
        mutate(language = language) %>%
        mutate(n_clusters = n_clusters) %>%
        select(language, n_clusters, everything())
    }
  }
  return(bind_rows(measurements))
}
```

@@

randomizations <- c("random_aoa", "to_nearest_aoa", "within_last_clustering")

@@

# measurements <- run_experiment(languages = languages,
#                           measures = measures,
#                           randomizations = randomizations,
#                           cluster_counts = 2:5,
#                           samples = 50)
# 
#saveRDS(measurements, "measurements.rds")

measurements <- readRDS("measurements.rds")

>>>>

```{r message=FALSE}
clusters_evolution <- function(vocab, n_clusters, min_age, max_age,
                               aoa_randomization, cluster_randomization = FALSE) {

  if(aoa_randomization == "none") {
    # do nothing
  } else if(aoa_randomization == "random_aoa") {
    vocab <- randomize_aoa(vocab) # TODO handle randomization, write "randomize_aoa"" in random_helper.r
  } else if(aoa_randomization == "to_nearest_aoa") {
    vocab <- randomize_aoa_to_nearest(vocab)
  } else if(aoa_randomization == "within_last_clustering") {
    vocab <- randomize_within_last_clustering(vocab, n_clusters)
  } else {
    stop("Randomization argument incorrect.")
  }

@@

  # list of cluster membership index vectors at each age
  membership_evo <- net_evo %>%
    map(w2v_walktrap) %>%
    map(~ cut_at(., no = n_clusters))

@@

  if(cluster_randomization) {
    clusters_evo <- map(clusters_evo, randomize_clustering)
  }

@@

measure_cluster_dynamics <- function(language, n_clusters, measures,
                                     aoa_randomizations, 
                                     cluster_randomizations, # c(TRUE, FALSE)
                                     samples) {
  vocab <- get_language_vocab(language)

@@

  # true vocabulary sizes (full vocabulary size at each month)
  measurements[[length(measurements) + 1]] <-
    tibble(age = min(vocab$age):max(vocab$age),
           measure = "true_vocab_size",
           aoa_randomization = NA, # same for all randomizations
           cluster_randomization = NA,
           sample = NA,
           value = min(vocab$age):max(vocab$age) %>%
             map(~ filter(vocab, age <= .)) %>%
             map(nrow) %>%
             unlist())

  # --------------------- measures that don't depend on randomizations --------------------- #
  true_clusters_evo <- clusters_evolution(vocab,
                                          n_clusters,
                                          min(vocab$age),
                                          max(vocab$age),
                                          aoa_randomization = "none",
                                          cluster_randomization = FALSE)

  # w2v vocabulary sizes (number of words know at each month in clustering)
  measurements[[length(measurements) + 1]] <-
    tibble(age = min(vocab$age):max(vocab$age),
           measure = "w2v_vocab_size",
           aoa_randomization = NA, # same for all randomizations
           cluster_randomization = NA,
           sample = NA,
           value = unlist(map(true_clusters_evo, ~ length(unlist(.)))))

  # --------------------- (optionally) randomized measures --------------------- #

  for (cluster_randomization in cluster_randomizations) {

    for (aoa_randomization in aoa_randomizations) {

      for (sample in 1:samples) {
        random_clusters_evo <- clusters_evolution(vocab,
                                                  n_clusters,
                                                  min(vocab$age),
                                                  max(vocab$age),
                                                  aoa_randomization = aoa_randomization,
                                                  cluster_randomization = cluster_randomization)

        for (measure in measures) {
          value <- run_measure(random_clusters_evo, measure)
          measurements[[length(measurements) + 1]] <-
            tibble(age = min(vocab$age):max(vocab$age),
                   measure = measure,
                   aoa_randomization = aoa_randomization,
                   cluster_randomization = cluster_randomization,
                   sample = sample,
                   value = value)
        }
      }
    }
  }

@@

run_experiment <- function(languages, measures, aoa_randomizations,
                           cluster_randomizations, cluster_counts, samples) {
  measurements = list()
  cat("measuring dynamics\n")
  for(language in languages) {
    cat("  language:", language, "\n")
    for(n_clusters in cluster_counts) {
      cat("    n_clusters: ", n_clusters, "\n")
      measurements[[length(measurements) + 1]] <- 
        measure_cluster_dynamics(language, n_clusters, measures,
                                 aoa_randomizations, cluster_randomizations, samples) %>%
        mutate(language = language) %>%
        mutate(n_clusters = n_clusters) %>%
        select(language, n_clusters, everything())
    }
  }
  return(bind_rows(measurements))
}
```

@@

aoa_randomizations <- c("none", "random_aoa", "to_nearest_aoa", "within_last_clustering")

cluster_randomizations <-  c(TRUE, FALSE)

@@

# measurements <- run_experiment(languages = languages,
#                           measures = measures,
#                           aoa_randomizations = randomizations,
#                           cluster_randomizations = c(FALSE)
#                           cluster_counts = 2:5,
#                           samples = 50)
# 
#saveRDS(measurements, "measurements.rds")

### compute cluster randomization measurements, TAKES A WHILE

cluster_randomization_measurements <- run_experiment(
                          languages = languages,
                          measures = measures,
                          aoa_randomizations = c("none"),
                          cluster_randomizations = c(TRUE, FALSE),
                          cluster_counts = 2:5,
                          samples = 50)

saveRDS(cluster_randomization_measurements, "cluster_randomization_measurements.rds")

measurements <- readRDS("measurements.rds")
cluster_randomization_measurements <- readRDS("cluster_randomization_measurements.rds")
```
